---
title: "W_UP_01"
author: "Wilhelmus Elersich"
date: "fall 2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

The skilled players do more pushups than the linemen. The skilled players also have greater variety in the amount of pushups done than the line players. The mean amount of pushups done by the line players is ~15, while the mean done by the skilled players is ~50.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
favstats(pushups~position,data=mydata)
```
The skilled players, on average, do ~3 times the amount of pushups that the line players do. The ratio of the minimum amount done by the line players to the skilled players is exactly 1:3, and the mean done by the skilled players is above the maximum done by the line players.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

The probability that there is no statistical difference between the number of pushups a line player can do and the number a skilled player can do is 0.000009421. This probability is so low that it can be safely ignored.

# Discussion and Conclusion

This problem was a categorical type problem, which only had two categories, line and skill. The t-test was used to determine the results. The numerical and graphical tests were also used, determining that the skilled players do more pushups than the line players. The t-test determined that the probability of no statistical difference between the groups was so small that it could be safely ignored.

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

